---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# megamation

<!-- badges: start -->

[![R-CMD-check](https://github.com/asadow/megamation/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/asadow/megamation/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

The goal of `megamation` is to facilitate Megamation data downloads in R. It wraps up the [Megamation REST API](https://apidocs.megamation.com/) so that each API endpoint (i.e. a URL with parameters) becomes an R function with documented arguments.

`megamation` also contains and implements functions to

-   Expose important details from HTTP errors in R errors.
-   Provide a paginate function for large downloads.
-   Caches responses to GET requests that have status code 200 and at least one of the standard caching headers (e.g. Expires, Etag, Last-Modified, Cache-Control)

## Installation

You can install the development version of `megamation` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("asadow/megamation")
```

## Authorization

Your Megamation representative will provide your key and URL. A helper function is provided to install these credentials (it creates name-value pairs in your `.Renviron` file, a safe place for secrets.) Edit and run the function below:

``` r
library(megamation)
mm_set_creds(
   key = "<YOUR-MEGAMATION_KEY>",
   url = "<YOUR-MEGAMATION_URL>",
   install = TRUE
   )
```

### Aside

You can set your own name-value pairs by using `Sys.setenv(NAME = "VALUE")`. For, example.

``` r
Sys.setenv(MEGAMATION_KEY = "R&RwillNeverDie")
Sys.setenv(MEGAMATION_URL = "https://api.megamation.com/uog/dl")
```

Alternatively you can open your `.Renviron` (`usethis::edit_r_environ()`) and enter each `NAME = "VALUE"` on separate lines.

## A simple request

TBD
```{r}
```

## Building a custom request

`mm_req()` allows you to define a request for any resource: `"timecard"`, `"workorder"`, etc.

```{r}
library(megamation)
req <- mm_req("timecard", date = I("<>09-01-2023,09-29-2023"))
```

You would normally run `httr2::req_perform()`. Here I run `httr2::req_dry_run()` to show exactly what `httr2` will send to the server, without actually sending it.

```{r}
req |> httr2::req_dry_run()
```
### Performing the request

A custom request can be performed using `httr2::req_perform()`. An API response is returned. As the body of the response is  unwieldy (it contains the data in an embedded list as raw bytes), the helper function `mm_resp_data()` returns the data.

```{r eval = FALSE}
resp <- req |> httr2::req_perform() 
resp |> mm_resp_data()
```

### Pagination

To add pagination, use `mm_req_paginate()` before the performance steps.

```{r eval = FALSE}
req |> mm_req_paginate() 
```

